---
title: "STAT 401"
author: "Zackary Scalyer"
date: "9/13/2020"
output:
  html_document:
    df_print: paged
---

<!-- use regular html style comments like this -->  
<!-- then we can make notes and comments that will not be included in the final document -->  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```
<!-- above is the first code chunck, starts with ```{}, and ends with ```
{r setup} this makes r as the code chunck engine with name setup, 
everything after the comma is for CHUNK OPTIONS, 
include=FALSE will not include the code in doc after running 
-->  


# Homework #2  
<!-- a level one headder starts with one # -->

Page 47-49  #1, 3, 4, 5, 11, 14, 16, 17, 19   
<!-- any test outside of a code chunck will be normal text in the final doc,
two spaces at the end of a line, or a empty line, will make a line brake in the final doc-->  

## Problem 1  
<!-- a level two headder starts with 2 #s -->  

> An experiment is conducted to determine the optimal time and temperature
combination for baking a cake. The response variable of interest is taste.
Four batches of cake will be baked separately at each combination of baking
times (25 and 30 minutes) and temperature settings (275 $^oF$, 300 $^oF$, and 325 $^oF$).

<!-- block quotes starts with >.
note that there is no spaces at the end of each line so the final document keeps the text together.-->  

```{r}
# inline comments in code chunck work the same as r normaly does
times = c(25,30)
temps = c(275,300,325)
combos = expand.grid(times,temps)
dat1 = data.frame(times,temps,'t'=combos[1:6,1],'T'=combos[1:6,2])
dat1
```

<!-- to insert an new code chunk press ctrl+alt+i -->

(a) What are the experimental units?  

The experimental units are the batches of cake

<!-- anything wrapted in $ is for LaTex expressions -->

[LaTeX ref link](https://en.wikibooks.org/wiki/LaTeX/Mathematics)  

<!-- you can link websites within the document. -->  

**I think your awanser for a is not correct**  

<!-- wrapping text with two * will make the text bold, one * will make text italc -->  

*An experimental unit is one member of a set of entities being studied. The experimental units here are batches of cake. We have 4 batches per combination of baking times and temp so we should have $4 \times 2 \times 3 = 24$ experimental units.*  

(b) What are the factors in this experiment?  

The factors in this experiment is time and temperature.  

(c) State the levels of each factor.  

The time has two levels, 25 and 30 minutes and the temperature has three levels, 275, 300 and 325 $^oF$.  

(d) List all the treatments in this experiment.  

There are not any treatments in this experiment since it is not a one-factor study.  

**I think your awanser for d is not correct**  

*Treatments are the combenations of the experimental factors of intrest. A a one-factor study means the factor levels and treatments are the same. A two-factor study has one treatment for each combentation of factor levels. Here we have six treatments.*  






